Tidy data structure to support exploration and modeling of temporal-context data

### 2018-11-14 main.Rmd
started on section 4.2

This tidy data representation choice will prove suitable for almost all conceivable applications of temporal data. Time-based pipeline starts with raw data. It is advised to scrutinize identical entries of key and index in the right beginning. Duplicates signal the data quality issue, which would likely affect the following analyses and hence decision making. Analysts are encouraged to gaze at data as earlier as possible and reason about the process of data cleaning. When the data meets the tsibble standard, it flows into the exploration stage.

@@

## Modularity and clarity

An individual operation that performs on a specific task can be phrased as a verb. This verb is self-explanatory enough to express what it is supposed to do or fail. We shall adapt **dplyr** key verbs to time domain and expand its vocabulary a little more to handle time-related analysis problems.

@@

## Composition and transparency

>>>>

This tidy data representation choice will prove suitable for almost all conceivable applications of temporal data. Time-based pipeline starts with raw data however it lands. It is advised to scrutinize identical entries of key and index in the right beginning. Duplicates signal the data quality issue, which would likely affect the following analyses and hence decision making. Analysts are encouraged to gaze at data as earlier as possible and reason about the process of data cleaning. When the data meets the tsibble standard, it flows into the exploration stage.

@@

## Clarity and transparency

Transformation assembles a set of modules. A unit that makes up a module is function or preferably "verb". A tsibble is an object, considered as a conceptualized and materialized noun, an action performed on the object can be phrased as a verb. Naming verbs is difficult. This verb is self-explanatory enough to express what it is supposed to do or fail. We shall adapt **dplyr** key verbs to time domain and expand its vocabulary a little more to handle time-related analysis problems.

@@

## Composition and modularity
